### 2014-09-19 fundamentals/impl.tex

Because this doesn't rely on PowerSim, GoldSim, Excel, or any other COTS 
Windows-based software, we can run singular instances of Cyclus 
on large linux machines that have lots more capability than hacked together 
Windows clusters.

@@

\subsection{Regions, Institutions, and Facilities}

\Cyclus provides a novel representation of entities in the nuclear fuel cycle,
including facilities, institutions managing those facilities, and regions. While
some simulators (TODO cite DESAE) have provided a notion of static regional
effects, \Cyclus allows for both regions and institutions to be first-class
actors in simulated fuel cycles.

>>>>

\Cyclus is primarily written in \texttt{C++}, and support is currently provided
for Linux-based (including Ubuntu and OSX) platforms. Furthermore, the core
infrastructure and related archetypes are free and open-source, BSD-3-clause
licsened. No part of \Cyclus is proprietary or based on commercial, off the
shelf (COTS) software. Accordingly, it can be easily deployed on large compute
systems, such as high-throughput computing (HTC) systems.

Cyclopts (\TODO{cite}), a proof of principle design and implementation of such a
system, uses UW-Madison's HTCondor HTC infrastructure to perform sensitivity
studies on \Cyclus' resource exchange optimization solvers. To date, it has been
used run over $10^4$ jobs, or (\TODO{compute time}) total compute hours, using
the \Cyclus library via its resource exchange API.

@@

\subsection{Region/Institution/Facility hierarchy}
% (diagram)
